Pyg4ometry: a python library for the creation of Monte Carlo radiation transport physical geometries

### 2020-01-03 public/paper/pyg4ometry.tex
More on g2f in paper

\section{Geant4 to FLUKA conversion}
It is relatively straight forward to convert Geant4 geometry to FLUKA. Each of the Geant4 solids can be mapped to a FLUKA CSG region.
Some solids in Geant4 directly map to a FLUKA body, others need a construction of a simple FLUKA CSG tree.

\begin{table}[hbt!]
\centering
\begin{tabular}{| l | l | } \hline
Geant4 solid			& FLUKA region constuction		\\ \hline
Box					& +2 XYP + 2 XZP + 2 YZP 		\\
Tube					& +ZCC - 2 XYP	 			\\
CutTube				& +ZCC - 2 PLA				\\
Cone				& +TRC -TRC - WED			\\
Para					& +ARB						\\
Trd					& +ARB						\\
Trap					& +ARB						\\
Sphere				& +SPH - SPH  - WED - TRC		\\
Orb					& +SPH						\\
Torus				& +$N$ ZCC  - $N$ PLA			\\
Polycone				& +$N$ ARB					\\
GenericPolycone		& +$N$ ARB					\\
Polyhedra				& +$N$ ARB					\\
Eltube				& +ZEC  - 2 XYP				\\
Ellipsoid				& +ELL - 2 XYP		 			\\
Elcone				& +QUA - 2 XYP				\\
Paraboloid			& +QUA - 2 XYP				\\
Hype					& +QUA - 2 XYP				\\
Tet					& +ARB						\\
Xtru					& +$N$ ARB					\\
TwistedBox			& +$N$ ARB					\\
TwistedTtap			& +$N$ ARB					\\
TwistedTrd			& +$N$ ARB				 	\\
TwistedTube			& +$N$ ARB					\\
Arb8					& +ARB						\\
Tessellated			& N/A					 	\\
Union				& | zone1 | zone2				\\
Subtraction			& +zone1 -zone2				\\
Intersection			& +zone1 +zone2				\\
MultiUnion			& | zone1 | zone2 | zone3 | ...	\\
ScaledSolid			& geant4.solid.ScaledSolid		\\ \hline				
\end{tabular}
\caption{GDML/Geant4 solids and the mapping to FLUKA bodies}
\end{table}

>>>>

\section{Geant4 to FLUKA conversion}
It is relatively straight forward to convert Geant4 geometry to FLUKA. Each of the Geant4 solids can be mapped to a FLUKA CSG zone.
Some solids in Geant4 directly map to a FLUKA body, others need a construction of a simple FLUKA CSG tree.

\begin{table}[hbt!]
\centering
\begin{tabular}{| l | l | } \hline
Geant4 solid			& FLUKA region constuction		\\ \hline
Box					& +2 XYP + 2 XZP + 2 YZP 		\\
Tube					& +ZCC - 2 PLA -2 XYP - ZCC	 	\\
CutTube				& +ZCC - 4 PLA -ZCC			\\
Cone				& +TRC - TRC - WED			\\
Para					& +ARB						\\
Trd					& +ARB						\\
Trap					& +ARB						\\
Sphere				& +SPH - SPH  - WED - TRC		\\
Orb					& +SPH						\\
Torus				& +$N$ ZCC  - $N$ PLA			\\
Polycone				& +$N$ ARB					\\
GenericPolycone		& +$N$ ARB					\\
Polyhedra				& +$N$ ARB					\\
Eltube				& +ZEC  - 2 XYP				\\
Ellipsoid				& +ELL - 2 XYP		 			\\
Elcone				& +QUA - 2 XYP				\\
Paraboloid			& +QUA - 2 XYP				\\
Hype					& +QUA - 2 XYP				\\
Tet					& +ARB						\\
Xtru					& +$N$ ARB					\\
TwistedBox			& +$N$ ARB					\\
TwistedTtap			& +$N$ ARB					\\
TwistedTrd			& +$N$ ARB				 	\\
TwistedTube			& +$N$ ARB					\\
Arb8					& +ARB						\\
Tessellated			& N/A					 	\\
Union				& | zone1 | zone2				\\
Subtraction			& +zone1 -zone2				\\
Intersection			& +zone1 +zone2				\\
MultiUnion			& | zone1 | zone2 | zone3 | ...	\\
ScaledSolid			& geant4.solid.ScaledSolid		\\ \hline				
\end{tabular}
\caption{GDML/Geant4 solids and the mapping to FLUKA bodies}
\end{table}
